A thermodynamic view of dusty protoplanetary disks

### 2017-07-01 result.tex

We first consider constant
midplane dust-to-gas ratios $\epsilon_0$ and characteristic thickness
$H_\epsilon$. Then the dust-to-gas ratio $\epsilon=\epsilon(z)$. In 
this limit any growing modes must be associated with the imposed
temperature gradient (see \S\ref{limits}). We are then studying the
effect of dust-loading on the VSI previously studied in pure gas
disks \citep[][\citetalias{lin15} in this section]{lin15}. In 
\S\ref{varHd} we allow $\p_r\epsilon\neq 0$, and in 
\S\ref{vert_mixed} we consider VSI driven entirely by radial
gradients in the dust-to-gas ratio (as discussed in
\S\ref{vert_mixed_theory}).

@@

In \S\ref{vert_mixed_theory} we found that for strictly isothermal
disks, a vertically-uniform dust-to-gas ratio can be unstable
if $d\epsilon/dr\neq0$.  
To demonstate this numerically we consider the
same disk as above but with $q=0$ and choose $H_\mathrm{d}$ such
that $H_\epsilon=10^3\Hg$. Then vertical shear $\p_z\Omega$ is 
attributed to the radially-varying dust-to-gas ratio (see
Eq. \ref{vshear2}).

We show unstable modes for this disk in
Fig. \ref{vert_mixed_modes}. In order to obtain appreciable growth   
rates, we needed to consider super-Solar metalicity $Z=0.03$ and high
radial wavenumber $k_x\Hg=1800$. As expected from the discussion in
\S\ref{vert_mixed_theory}, the disk admits purely growing modes with
$\omega=0$. This is distinct from the growing oscillations associated
with classic VSI discussed above.

>>>>

We first consider constant
midplane dust-to-gas ratios $\epsilon_0$ and characteristic thickness
$H_\epsilon$. Then the dust-to-gas ratio $\epsilon=\epsilon(z)$. In 
this limit any growing modes must be associated with the imposed
temperature gradient (see \S\ref{limits}). We are then studying the
effect of dust-loading on the VSI previously studied in pure gas
disks \citep[][\citetalias{lin15} in this section]{lin15}. In 
\S\ref{varHd} we allow $\p_r\epsilon\neq 0$, and in 
\S\ref{vert_mixed} we consider VSI driven entirely by radial
gradients in the dust-to-gas ratio (as discussed in
\S\ref{iso_perfect}).

@@

In \S\ref{iso_perfect} we found that for strictly isothermal
disks, a vertically-uniform dust-to-gas ratio can be unstable
if $d\epsilon/dr\neq0$.  
To demonstate this numerically we consider the
same disk as above but with $q=0$ and choose $H_\mathrm{d}$ such
that $H_\epsilon=10^3\Hg$. Then vertical shear $\p_z\Omega$ is 
attributed to the radially-varying dust-to-gas ratio (see
Eq. \ref{vshear2}).

We show unstable modes for this disk in
Fig. \ref{vert_mixed_modes}. In order to obtain appreciable growth   
rates, we needed to consider super-Solar metalicity $Z=0.03$ and high
radial wavenumber $k_x\Hg=1800$. As expected from the discussion in
\S\ref{iso_perfect}, the disk admits purely growing modes with
$\omega=0$. This is distinct from the growing oscillations associated
with classic VSI discussed above.
